Distributed multi-objective evolutionary optimization using island-based selective operator application

### 2019-05-20 hpmoon-asoco.tex
More changes by julio

Real-world MOPs usually require a high number of decision variables \cite{Zhang17DECAL,XU2018268}, 
meaning that the
MOEAs need to deal with large individuals \textcolor{blue}{representing those variables} and spend significant extra
time \textcolor{blue}{applying the} crossover, mutation and migration \textcolor{blue}{operators}.
% If this is the only justification, it should have been assessed at the end. It would be better if it was qualified, in the sense that more exploration is needed or something like that - JJ
Different authors have 
proposed methods to divide the decision space (the chromosome) to
improve the performance and solution quality. % Why should it improve quality? - JJ Pablo: look at the 2 new paragraphs sent by Julio below (between \begin{bluecolor})
In this aspect, the
co-evolution model is a dimension-distributed model where a 
high-dimensional problem is divided into lower dimensional ones
\citep{Gong15models,Tonda12cooperative}, and evolved separately. \textcolor{blue}{To evolve the individuals of a subpopulation, the processor where it has been allocated can operate according to two main alternatives.} One
example of the application of the \textcolor{blue}{first alternative} was described in
\citep{Kimovski15Parallel}. The method presented in that work involves
different workers that evolve sub-populations created and recombined
by a master process, which performs \textcolor{blue}{different alternatives for the recombinattion/cooperation of the subpopulations returned by worker processes}. A high
dimensional problem was used to compare these 
alternatives\textcolor{blue}{; also, i}n \citep{Dorronsoro13superlinear}, a distributed
co-evolutionary island model was used.  Although  both papers \textcolor{blue}{described}
significant speedups, only a \textcolor{blue}{small} number of nodes were
employed (8). However, when the number of islands is increased, the division
of each section of the chromosome becomes smaller, and the scalability
may be affected by obtaining lower quality solutions in the same
amount of time. \textcolor{blue}{Moreover, in this first alternative, each processor only works with the variables of the individuals in its population. Thus, only whenever the cost function is decomposable in such a way that the variables allocated to different processors are not interdependent, the evaluation of the fitness of an individual in the population can be done by composing the cost evaluated separately by each processor from the values of the variables allocated to it. Otherwise, it has to be determined after composing the whole solution from the components allocated to each processor the components of the solutions in the subpopulations.}

>>>>

Real-world MOPs usually require a high number of decision variables \cite{Zhang17DECAL,XU2018268}, 
meaning that the
MOEAs need to deal with large individuals \textcolor{blue}{representing those variables} and spend significant extra
time \textcolor{blue}{applying the} crossover, mutation and migration \textcolor{blue}{operators}.
% If this is the only justification, it should have been assessed at the end. It would be better if it was qualified, in the sense that more exploration is needed or something like that - JJ
Different authors have 
proposed methods to divide the decision space (the chromosome) to
improve the performance and solution quality. % Why should it improve quality? - JJ Pablo: look at the 2 new paragraphs sent by Julio below (between \begin{bluecolor})
In this aspect, the
co-evolution model is a dimension-distributed model where a 
high-dimensional problem is divided into lower dimensional ones
\citep{Gong15models,Tonda12cooperative}, and evolved separately. \textcolor{blue}{To evolve the individuals of a subpopulation, the processor where it has been allocated can operate according to two main alternatives.} One
example of the application of the \textcolor{blue}{first alternative} was described in
\citep{Kimovski15Parallel}. The method presented in that work involves
different workers that evolve sub-populations created and recombined
by a master process, which performs \textcolor{blue}{different alternatives for the recombinattion/cooperation of the subpopulations returned by worker processes}. A high
dimensional problem was used to compare these 
alternatives\textcolor{blue}{; also, i}n \citep{Dorronsoro13superlinear}, a distributed
co-evolutionary island model was used.  Although  both papers \textcolor{blue}{described}
significant speedups, only a \textcolor{blue}{small} number of nodes were
employed (8). However, when the number of islands is increased, the division
of each section of the chromosome becomes smaller, and the scalability
may be affected by obtaining lower quality solutions in the same
amount of time. \textcolor{blue}{Moreover, in this first alternative, each processor only works with the variables of the individuals in its population. Thus, only whenever the cost function is decomposable in such a way that the variables allocated to different processors are not interdependent, the evaluation of the fitness of an individual in the population can be done by composing the cost evaluated separately by each processor from the values of the variables allocated to it. Otherwise, it has to be determined after composing the whole solution from the components allocated to each processor the components of the solutions in the subpopulations. In fact, different strategies to define the way to distribute the components into groups to be allocated to the available processors are required. They have been mainly defined according to three categories \cite{Jia19Coevo}: (1) static partitions of variables into groups; (2) random dynamic grouping that changes the variables among groups along the optimization process; and (3) learning-based dynamic grouping to distribute the components by applying techniques to detect the interdependence among variables along the process. }
